SI

### 2021-03-01 ms/manuscript.Rmd
Update data cleaning, MS, SI
- Include C. apiifolia 2012 NaCl data
- Change C. minutum DT data to var 2 for both 2012 and 2014 (as confirmed by checking lab and field notes)
- Add times for all NaCl plots in SI

# Extract effect of generation on DT from GLMM
sporo_dt_effect_mean <-
glmm_params %>% 
  filter(response == "recovery") %>%
  verify(predictor == "generationsporophyte") %>%
  pull(post.mean) %>%
  scales::percent(accuracy = 0.1)

sporo_dt_effect_lower <-
glmm_params %>% 
  filter(response == "recovery") %>%
  verify(predictor == "generationsporophyte") %>%
  pull(`l-95% CI`) %>%
  scales::percent(accuracy = 0.1)

sporo_dt_effect_upper <-
glmm_params %>% 
  filter(response == "recovery") %>%
  verify(predictor == "generationsporophyte") %>%
  pull(`u-95% CI`) %>%
  scales::percent(accuracy = 0.1)

t_test_results

@@

```{r sporo-dt-disc-stats}
# Calculate the avg daily maximum VPD tolerated by sax & terr sporophytes
max_ter_vpd <- mean_vpd_sporo %>%
  left_join(filmy_habit) %>%
  filter(habit %in% c("Saxicolous", "Terrestrial")) %>%
  slice_max(order_by = vpd_sporophyte_mean) %>%
  pull(vpd_sporophyte_mean) %>%
  round(1)
```

>>>>

# Extract effect of generation on DT from GLMM
sporo_dt_effect_mean <-
glmm_params %>% 
  filter(response == "recovery", pMCMC < 0.05) %>%
  verify(predictor == "generationsporophyte") %>%
  pull(post.mean) %>%
  scales::percent(accuracy = 0.1)

sporo_dt_effect_lower <-
glmm_params %>% 
  filter(response == "recovery", pMCMC < 0.05) %>%
  verify(predictor == "generationsporophyte") %>%
  pull(`l-95% CI`) %>%
  scales::percent(accuracy = 0.1)

sporo_dt_effect_upper <-
glmm_params %>% 
  filter(response == "recovery", pMCMC < 0.05) %>%
  verify(predictor == "generationsporophyte") %>%
  pull(`u-95% CI`) %>%
  scales::percent(accuracy = 0.1)

@@

```{r sporo-dt-disc-stats}
# Calculate the avg daily maximum VPD tolerated by sax & terr sporophytes
max_ter_vpd <- mean_vpd_sporo %>%
  left_join(filmy_habit, by = "species") %>%
  filter(habit %in% c("Saxicolous", "Terrestrial")) %>%
  slice_max(order_by = vpd_sporophyte_mean) %>%
  pull(vpd_sporophyte_mean) %>%
  round(1)
```

### 2021-03-01 ms/si.Rmd
Update data cleaning, MS, SI
- Include C. apiifolia 2012 NaCl data
- Change C. minutum DT data to var 2 for both 2012 and 2014 (as confirmed by checking lab and field notes)
- Add times for all NaCl plots in SI

@@

```{r sporophyte-dt-NaCl, fig.height = 6.5, fig.width = 9, fig.cap = ""}
# Subset desiccation duration data
# H_polyanthos shows n=1, but this is only because pre/post were available for only one sample
# (actually had 8 samples total)
nacl_clusters_2013 <- 
  sporo_times %>%
  filter(str_detect(dataset, "2013")) %>%
  cluster_sporo_times("NaCl", 4) %>%
  mutate(
    serial_no = case_when(
      species %in% c("Didymoglossum_tahitense", "Crepidomanes_kurzii", "Callistopteris_apiifolia") & dry_time == "2" ~ "missing",
      species %in% c("Hymenophyllum_multifidum", "Hymenophyllum_digitatum") ~ "10140667",
      species %in% c("Hymenophyllum_polyanthos") ~ "10152774",
      species %in% c("Abrodictyum_dentatum") & dry_time == "2" ~ "missing",
      TRUE ~ "missing"
    ),
    serial_no = as.factor(serial_no)
  )

nacl_clusters_2014 <-
  sporo_times %>%
  filter(str_detect(dataset, "2014")) %>%
  cluster_sporo_times("NaCl", 1) %>%
  mutate(
    serial_no = case_when(
      species %in% c("Vandenboschia_maxima") & dry_time == "2" ~ "10140661",
      TRUE ~ "10152773"
    ),
    serial_no = as.factor(serial_no)
  )

# make levels of `serial_no` and `species` the same across datasets
nacl_all_sn <- filmy_dt_chamber %>% 
  filter(salt == "NaCl") %>% 
  pull(serial_no) %>% 
  unique %>% 
  sort %>%
  c("missing")

nacl_all_species <- sporo_times %>% 
  filter(salt == "NaCl") %>% 
  pull(species) %>% 
  unique %>% 
  sort

nacl_clusters_2013 <- mutate(
  nacl_clusters_2013, 
  # sort SN in numeric order
  serial_no = fct_expand(serial_no, nacl_all_sn) %>% fct_inseq,
  # sort species in reverse-alphabetical order (so 'A' is on top in plot)
  species = fct_expand(species, nacl_all_species) %>% fct_relevel(function (x) sort(x, decreasing = TRUE))
)

nacl_clusters_2014 <- mutate(
  nacl_clusters_2014, 
  serial_no = fct_expand(serial_no, nacl_all_sn) %>% fct_inseq,
  species = fct_expand(species, nacl_all_species) %>% fct_relevel(function (x) sort(x, decreasing = TRUE))
)

# Calculate time range for the clustered data
# to standardize x-axis
nacl_time_range_2013 <- c(min = min(nacl_clusters_2013$pre), max = max(nacl_clusters_2013$post))
nacl_time_range_2014 <- c(min = min(nacl_clusters_2014$pre), max = max(nacl_clusters_2014$post))

# Subset DT chamber data
nacl_chamber_data_2012 <- 
  filmy_dt_chamber %>% 
  filter(salt == "NaCl", date_time > "2012-07-31 18:10:00 UTC", date_time < "2013-01-01 00:10:00 UTC")

nacl_time_range_2012 <- c(min = min(nacl_chamber_data_2012$date_time), max = max(nacl_chamber_data_2012$date_time))

nacl_chamber_data_2013 <-
  filter(filmy_dt_chamber, 
         date_time >= nacl_time_range_2013[["min"]], 
         date_time <= nacl_time_range_2013[["max"]], 
         salt == "NaCl")

nacl_chamber_data_2014 <- 
  filter(filmy_dt_chamber, 
         date_time >= nacl_time_range_2014[["min"]], 
         date_time <= nacl_time_range_2014[["max"]], 
         salt == "NaCl") %>%
  mutate(
    # There are two sets of times: 2014-06-17 to 2014-07-02, and 2014-07-06 to 2014-07-08
    # Add a group for these so ggplot doesn't connect lines betweeen them
    day = yday(date_time),
    group = ifelse(day < 185, "a", "b")
  )

# Get overall range of temperature and RH for NaCl
# to standardize y-axis
nacl_temp_range <- filter(filmy_dt_chamber, salt == "NaCl") %>%
  summarize(min = min(temp), max = max(temp)) %>%
  pivot_longer(everything()) %>%
  arrange(value) %>%
  pull(value)

nacl_rh_range <- filter(filmy_dt_chamber, salt == "NaCl") %>%
  mutate(rh = rh * 0.01) %>%
  summarize(min = min(rh), max = max(rh)) %>%
  pivot_longer(everything()) %>%
  arrange(value) %>%
  pull(value)

# Set up color palette for serial numbers
serial_no_cols <- c(
  brewer_pal(palette = "Dark2")(5),
  "grey20") %>%
  set_names(
    bind_rows(nacl_chamber_data_2013, nacl_chamber_data_2014) %>%
      filter(serial_no != "missing") %>%
      pull(serial_no) %>%
      unique %>%
      sort %>%
      c("missing")
  )

# Time plots
nacl_time_plot_2013 <- 
  ggplot(
    nacl_clusters_2013, 
    aes(
      x = species, ymin = pre, ymax = post, y = post, 
      group = species_duration, color = serial_no)
  ) +
  geom_linerange(position = position_dodge(0.5)) +
  geom_point(position = position_dodge(0.5)) +
  scale_y_datetime(limits = nacl_time_range_2013) +
  # Print all 'species' on the y-axis using `drop = false`
  scale_x_discrete(labels = str_abbrev_sp_pretty, drop = FALSE) +
  # Print all levels of 'serial no' in the legend using `drop = false`
  scale_color_manual(values = serial_no_cols, drop = FALSE) +
  labs(x = "Species", color = "Serial no.") +
  coord_flip() +
  theme(
    axis.title = element_blank(),
    axis.text.y = element_blank())

nacl_time_plot_2014 <- 
  ggplot(
    nacl_clusters_2014, 
    aes(x = species, ymin = pre, ymax = post, y = post, 
        group = species_duration, color = serial_no)
  ) +
  geom_linerange(position = position_dodge(0.5)) +
  geom_point(position = position_dodge(0.5)) +
  scale_y_datetime(limits = nacl_time_range_2014) +
  scale_x_discrete(labels = str_abbrev_sp_pretty, drop = FALSE) +
  scale_color_manual(values = serial_no_cols) +
  coord_flip() +
  labs(x = "Species", color = "Serial no.") +
  theme(
    axis.title = element_blank(),
    axis.text.y = element_markdown()) +
  guides(color = "none")

# RH plots
nacl_rh_plot_2012 <- 
  ggplot(
    nacl_chamber_data_2012, 
    aes(x = date_time, y = 0.01*rh)
  ) +
  geom_line(size = 0.25) +
  scale_x_datetime(limits = nacl_time_range_2012) +
  scale_y_continuous(
    label = scales::label_percent(accuracy = 1), 
    limits = nacl_rh_range) +
  labs(
    y = "Relative humidity",
    color = "Serial no.") +
  guides(color = "none") +
  theme(axis.title.x = element_blank()) +
  blank_y_theme()

nacl_rh_plot_2013 <- 
  ggplot(
    nacl_chamber_data_2013, 
    aes(x = date_time, y = 0.01*rh, color = serial_no)
  ) +
  scale_color_manual(values = serial_no_cols) +
  geom_line(size = 0.25) +
  scale_x_datetime(limits = nacl_time_range_2013) +
  scale_y_continuous(
    label = scales::label_percent(accuracy = 1), 
    limits = nacl_rh_range) +
  labs(
    y = "Relative humidity",
    color = "Serial no.") +
  theme(
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()) +
  blank_y_theme() +
  guides(color = "none")

nacl_rh_plot_2014 <- 
  ggplot(
    nacl_chamber_data_2014, 
    aes(x = date_time, y = 0.01*rh, color = serial_no, group = interaction(group, serial_no))
  ) +
  scale_color_manual(values = serial_no_cols) +
  geom_line(size = 0.25) +
  scale_x_datetime(limits = nacl_time_range_2014) +
  scale_y_continuous(
    label = scales::label_percent(accuracy = 1), 
    limits = nacl_rh_range) +
  labs(
    y = "Relative humidity",
    color = "Serial no.") +
  theme(
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()) +
  guides(color = "none")

# Temp plots
nacl_temp_plot_2012 <- 
  ggplot(
    nacl_chamber_data_2012, 
    aes(x = date_time, y = temp)
  ) +
  geom_line(size = 0.25) +
  scale_x_datetime(limits = nacl_time_range_2012) +
  scale_y_continuous(
    label = label_number(suffix = "\u00b0C", accuracy = 1), 
    limits = nacl_temp_range) +
  labs(
    y = "Temperature",
    color = "Serial no.",
    title = "2012") +
  theme(
    plot.title = element_text(hjust = 0.5, size = 11),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()) +
  blank_y_theme() +
  guides(color = "none")

nacl_temp_plot_2013 <- 
  ggplot(
    nacl_chamber_data_2013, 
    aes(x = date_time, y = temp, color = serial_no)
  ) +
  geom_line(size = 0.25) +
  scale_color_manual(values = serial_no_cols) +
  scale_x_datetime(limits = nacl_time_range_2013) +
  scale_y_continuous(
    label = label_number(suffix = "\u00b0C", accuracy = 1), 
    limits = nacl_temp_range) +
  labs(
    y = "Temperature",
    color = "Serial no.",
    title = "2013") +
  theme(
    plot.title = element_text(hjust = 0.5, size = 11),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()) +
  blank_y_theme() +
  guides(color = "none")

nacl_temp_plot_2014 <- 
  ggplot(
    nacl_chamber_data_2014, 
    aes(x = date_time, y = temp, color = serial_no, group = interaction(group, serial_no))
  ) +
  scale_color_manual(values = serial_no_cols) +
  geom_line(size = 0.25) +
  scale_x_datetime(limits = nacl_time_range_2014) +
  scale_y_continuous(
    label = label_number(suffix = "\u00b0C", accuracy = 1), 
    limits = nacl_temp_range) +
  labs(
    y = "Temperature",
    color = "Serial no.",
    title = "2014") +
  theme(
    plot.title = element_text(hjust = 0.5, size = 11),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()) +
  guides(color = "none")

nacl_temp_plot_2014 + nacl_temp_plot_2013 + nacl_temp_plot_2012 +
  nacl_rh_plot_2014 + nacl_rh_plot_2013 + nacl_rh_plot_2012 +
  nacl_time_plot_2014 + nacl_time_plot_2013 + plot_spacer() +
  plot_layout(ncol = 3, nrow = 3, guides = "collect") +
  plot_annotation(title = "c") &
  theme(
    plot.tag = element_text(face = "bold"),
    legend.position = "bottom")
```

@@

**`r s_figure("chamber")`**. Temperature, relative humidity (RH), and duration of desiccation treatment of filmy ferns from Moorea, French Polynesia. **a**--**c**, sporophytes; **d**, gametophytes. Relative humidity was controlled by placing drying salts inside desiccation chambers: **a**, LiCl (-282 MPa, 18 % RH); **b**, **d**, Mg(NO~3~)~2~ (-86 MPa, 58 % RH); **c**, NaCl (-38 MPa, 80 % RH). Temperature and RH measured with Track-It RH/Temp dataloggers logging every 10 min (2012) or Hobo ProV2 dataloggers logging every 5 min (2013, 2014). For **c**, multiple chambers were set up and tracked with different data loggers; serial number of data logger indicated by color; "missing" indicates data were not collected on the correspondence between samples and data loggers (chambers). For bottom-most panels (duration of desiccation treatment), line indicates duration of treatment and point indicates removal of sample from chamber. Gametophytes were measured in batches; membership of individual gametophytes to each batch can be found in `r s_table("gameto-batches")` (Online Resource 2).

>>>>

# NaCl plots need separate funcs because they involve color by serial number
make_nacl_time_plot <- function (data, serial_no_cols, time_limits) {
  ggplot(
    data, 
    aes(
      x = species, ymin = pre, ymax = post, y = post, 
      group = species_duration, color = serial_no)
  ) +
  geom_linerange(position = position_dodge(0.5)) +
  geom_point(position = position_dodge(0.5)) +
  scale_y_datetime(limits = time_limits, minor_breaks = "1 day") +
  # Print all 'species' on the y-axis using `drop = false`
  scale_x_discrete(labels = str_abbrev_sp_pretty, drop = FALSE) +
  # Print all levels of 'serial no' in the legend using `drop = false`
  scale_color_manual(values = serial_no_cols, drop = FALSE) +
  labs(x = "Species", color = "Serial no.") +
  coord_flip() +
  theme(
    axis.title = element_blank(),
    axis.text.y = element_markdown()
    )
}

make_nacl_rh_plot <- function(data, serial_no_cols, time_range, rh_range, groups = FALSE) {

  # If groups is TRUE, plot separate lines for different groups of data
  p <- if(groups == TRUE) {
    ggplot(
      data, 
      aes(x = date_time, y = 0.01*rh, color = serial_no, group = interaction(group, serial_no))
    ) 
  } else {
    ggplot(
      data, 
      aes(x = date_time, y = 0.01*rh, color = serial_no)
    )
  }

  p +
  geom_line(size = 0.25) +
  scale_color_manual(values = serial_no_cols) +
  scale_x_datetime(limits = time_range, minor_breaks = "1 day") +
  scale_y_continuous(
    label = scales::label_percent(accuracy = 1), 
    limits = rh_range) +
  labs(
    y = "Relative humidity",
    color = "Serial no.") +
  guides(color = "none") +
  theme(axis.title.x = element_blank()) +
  guides(color = "none")
}

make_nacl_temp_plot <- function(data, serial_no_cols, time_range, temp_range, title, groups = FALSE) {

  # If groups is TRUE, plot separate lines for different groups of data
  p <- if(groups == TRUE) {
    ggplot(
      data, 
      aes(x = date_time, y = temp, color = serial_no, group = interaction(group, serial_no))
    ) 
  } else {
    ggplot(
      data, 
      aes(x = date_time, y = temp, color = serial_no)
    )
  }

  p +
  geom_line(size = 0.25) +
  scale_color_manual(values = serial_no_cols) +
  scale_x_datetime(limits = time_range, minor_breaks = "1 day") +
  scale_y_continuous(
    label = label_number(suffix = "\u00b0C", accuracy = 1), 
    limits = temp_range) +
  labs(
    y = "Temperature",
    color = "Serial no.",
    title = title) +
  theme(
    plot.title = element_text(hjust = 0.5, size = 11),
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()) +
  guides(color = "none")
}

@@

```{r sporophyte-dt-NaCl, fig.height = 6.5, fig.width = 9, fig.cap = ""}
# Subset desiccation duration data
nacl_clusters_2012 <- filter(sporo_dt_times, salt == "NaCl") %>%
  mutate(
    serial_no = case_when(
      species %in% c(
        "Hymenophyllum_polyanthos", "Crepidomanes_humile", 
        "Crepidomanes_bipunctatum", "Polyphlebium_endlicherianum", 
        "Crepidomanes_minutum2") ~ "3200919",
      species == "Callistopteris_apiifolia" ~ "10140667, 10140659",
      TRUE ~ NA_character_
    )
  ) %>%
  mutate(year = "2012", species_duration = paste(species, dry_time))

# H_polyanthos shows n=1, but this is only because pre/post were available for only one sample
# (actually had 8 samples total)
nacl_clusters_2013 <- 
  sporo_times %>%
  filter(str_detect(dataset, "2013")) %>%
  cluster_sporo_times("NaCl", 4) %>%
  # Exclude A. dentatum, which is lacking chamber datalogger data
  filter(species != "Abrodictyum_dentatum") %>%
  mutate(
    serial_no = case_when(
      species %in% c("Didymoglossum_tahitense", "Crepidomanes_kurzii", "Callistopteris_apiifolia") & dry_time == "2" ~ "missing",
      species %in% c("Hymenophyllum_multifidum", "Hymenophyllum_digitatum") ~ "10140667",
      species %in% c("Hymenophyllum_polyanthos") ~ "10152774",
      TRUE ~ "missing"
    )
  ) %>%
  mutate(year = "2013")

nacl_clusters_2014 <-
  sporo_times %>%
  filter(str_detect(dataset, "2014")) %>%
  cluster_sporo_times("NaCl", 1) %>%
  mutate(
    serial_no = case_when(
      species %in% c("Vandenboschia_maxima") & dry_time == "2" ~ "10140661",
      TRUE ~ "10152773"
    )
  ) %>%
  mutate(year = "2014")

# Calculate time range for the clustered data
# to standardize x-axis
nacl_time_range_2012 <- c(min = min(nacl_clusters_2012$pre), max = max(nacl_clusters_2012$post))
nacl_time_range_2013 <- c(min = min(nacl_clusters_2013$pre), max = max(nacl_clusters_2013$post))
nacl_time_range_2014 <- c(min = min(nacl_clusters_2014$pre), max = max(nacl_clusters_2014$post))

nacl_chamber_data_2012 <-
  filmy_dt_chamber %>%
  mutate(year = as.character(year)) %>%
  filter(
    date_time >= nacl_time_range_2012[["min"]], 
    date_time <= nacl_time_range_2012[["max"]], 
    salt == "NaCl")

nacl_chamber_data_2013 <-
  filmy_dt_chamber %>%
  mutate(year = as.character(year)) %>%
  filter( 
    date_time >= nacl_time_range_2013[["min"]], 
    date_time <= nacl_time_range_2013[["max"]], 
    salt == "NaCl")

nacl_chamber_data_2014 <- 
  filmy_dt_chamber %>%
  mutate(year = as.character(year)) %>%
  filter( 
    date_time >= nacl_time_range_2014[["min"]], 
    date_time <= nacl_time_range_2014[["max"]], 
    salt == "NaCl") %>%
  mutate(
    # There are two sets of times: 2014-06-17 to 2014-07-02, and 2014-07-06 to 2014-07-08
    # Add a group for these so ggplot doesn't connect lines betweeen them
    day = yday(date_time),
    group = ifelse(day < 185, "a", "b")
  )

# Set up color palette for serial numbers
serial_no_cols <- c(
  brewer_pal(palette = "Dark2")(8),
  "grey20") %>%
  set_names(
    bind_rows(
      nacl_clusters_2012, nacl_clusters_2013, nacl_clusters_2014, 
      nacl_chamber_data_2012, nacl_chamber_data_2013, nacl_chamber_data_2014) %>%
      filter(serial_no != "missing", !is.na(serial_no)) %>%
      pull(serial_no) %>%
      unique %>%
      sort %>%
      c("missing")
  )

# Combine NaCl data so that factor levels are same across years
nacl_chamber_data <- bind_rows(nacl_chamber_data_2012, nacl_chamber_data_2013, nacl_chamber_data_2014) %>%
  mutate(
    year = as.character(year),
    serial_no = as.factor(serial_no) %>% 
      fct_expand(names(serial_no_cols)) %>% 
      fct_relevel(function (x) sort(x, decreasing = TRUE)) %>%
      fct_relevel("10140667, 10140659", after = Inf) %>%
      fct_relevel("missing", after = Inf))

nacl_clusters <- bind_rows(nacl_clusters_2012, nacl_clusters_2013, nacl_clusters_2014) %>%
  mutate(
    species = as.factor(species) %>% fct_relevel(function (x) sort(x, decreasing = TRUE)),
    serial_no = as.factor(serial_no) %>% 
      fct_expand(names(serial_no_cols)) %>% 
      fct_relevel(function (x) sort(x, decreasing = TRUE)) %>%
      fct_relevel("10140667, 10140659", after = Inf) %>%
      fct_relevel("missing", after = Inf))

# Get overall range of temperature and RH for NaCl
# to standardize y-axis
nacl_temp_range <- nacl_chamber_data %>%
  summarize(min = min(temp), max = max(temp)) %>%
  pivot_longer(everything()) %>%
  arrange(value) %>%
  pull(value)

nacl_rh_range <- nacl_chamber_data %>%
  mutate(rh = rh * 0.01) %>%
  summarize(min = min(rh), max = max(rh)) %>%
  pivot_longer(everything()) %>%
  arrange(value) %>%
  pull(value)

# Time plots
nacl_time_plot_2012 <- make_nacl_time_plot(
  nacl_clusters %>% filter(year == "2012"), serial_no_cols, nacl_time_range_2012)

nacl_time_plot_2013 <- make_nacl_time_plot(
  nacl_clusters %>% filter(year == "2013"), serial_no_cols, nacl_time_range_2013) +
  blank_y_theme() +
  guides(color = "none")

nacl_time_plot_2014 <- make_nacl_time_plot(
  nacl_clusters %>% filter(year == "2014"), serial_no_cols, nacl_time_range_2014) +
  blank_y_theme() +
  guides(color = "none")

# RH plots
nacl_rh_plot_2012 <- make_nacl_rh_plot(
  nacl_chamber_data %>% filter(year == "2012"),
  serial_no_cols,
  nacl_time_range_2012, 
  nacl_rh_range
)

nacl_rh_plot_2013 <- make_nacl_rh_plot(
  nacl_chamber_data %>% filter(year == "2013"),
  serial_no_cols,
  nacl_time_range_2013, 
  nacl_rh_range
) + 
  blank_y_theme() +
  blank_x_theme()

nacl_rh_plot_2014 <- make_nacl_rh_plot(
  nacl_chamber_data %>% filter(year == "2014"),
  serial_no_cols,
  nacl_time_range_2014, 
  nacl_rh_range,
  groups = TRUE
) + 
  blank_y_theme() +
  blank_x_theme()

# Temp plots
nacl_temp_plot_2012 <- make_nacl_temp_plot(
  nacl_chamber_data %>% filter(year == "2012"),
  serial_no_cols,
  nacl_time_range_2012, 
  nacl_temp_range,
  title = "2012") +
  guides(color = "none")

nacl_temp_plot_2013 <- make_nacl_temp_plot(
  nacl_chamber_data %>% filter(year == "2013"),
  serial_no_cols,
  nacl_time_range_2013, 
  nacl_temp_range,
  title = "2013") + 
  blank_y_theme() +
  blank_x_theme()

nacl_temp_plot_2014 <- make_nacl_temp_plot(
  nacl_chamber_data %>% filter(year == "2014"),
  serial_no_cols,
  nacl_time_range_2014, 
  nacl_temp_range,
  title = "2014",
  groups = TRUE) + 
  blank_y_theme() +
  blank_x_theme()

# Combine plots
nacl_temp_plot_2012 + nacl_temp_plot_2013 + nacl_temp_plot_2014 +
  nacl_rh_plot_2012 + nacl_rh_plot_2013 + nacl_rh_plot_2014 +
  nacl_time_plot_2012 + nacl_time_plot_2013 + nacl_time_plot_2014 +
  plot_layout(ncol = 3, nrow = 3, guides = "collect") +
  plot_annotation(title = "c") &
  theme(
    plot.tag = element_text(face = "bold"),
    legend.position = "bottom")
```

@@

**`r s_figure("chamber")`**. Temperature, relative humidity (RH), and duration of desiccation treatment of filmy ferns from Moorea, French Polynesia. **a**--**c**, sporophytes; **d**, gametophytes. Relative humidity was controlled by placing drying salts inside desiccation chambers: **a**, LiCl (-282 MPa, 18 % RH); **b**, **d**, Mg(NO~3~)~2~ (-86 MPa, 58 % RH); **c**, NaCl (-38 MPa, 80 % RH). Temperature and RH measured with Track-It RH/Temp dataloggers logging every 10 min (2012 species other than *Callistopteris apiifolia*) or Hobo ProV2 dataloggers logging every 5 min (2012 *Callistopteris apiifolia*, 2013, 2014). For NaCl (**c**), multiple chambers were set up and tracked with different data loggers; serial number of data logger indicated by color; "missing" indicates correspondence between samples and data loggers (chambers) unknown. For bottom-most panels (duration of desiccation treatment), line indicates duration of treatment and point indicates removal of sample from chamber. Gametophytes were measured in batches; membership of individual gametophytes to each batch can be found in `r s_table("gameto-batches")` (Online Resource 2).
